On the Limitations of Weighted Model Counting

### 2020-04-02 paper.tex
Sums of BAs

>>>>

\section{Implications for Lifted Inference}

\begin{definition}
  Given a BA $\mathbf{A}$, a \emph{subalgebra} is a subset $\mathbf{B} \subseteq
  \mathbf{A}$ that, together with the operations, zero, and one of $\mathbf{A}$,
  is a BA.
\end{definition}

\begin{definition}
  Let $\mathbf{A},$ $\mathbf{B}$, and $\mathbf{C}$ be BAs such that $\mathbf{B}$
  is a subalgebra of $\mathbf{A}$. Let $f\colon \mathbf{A} \to \mathbf{C}$ and
  $g\colon \mathbf{B} \to \mathbf{C}$ be homomorphisms. Then $f$ is an
  \emph{extension} of $g$ if $f(x) = g(x)$ for all $x \in \mathbf{B}$. If $f$ is
  an extension of each member of a family $\{ g_i \}_{i \in I}$ of
  homomorphisms, then $f$ is called a \emph{common extension} of $\{ g_i \}_{i
    \in I}$.
\end{definition}

\begin{definition}
  Let $\{ \mathbf{A}_i \}_{i \in I}$ be a family of subalgebras of a BA
  $\mathbf{A}$ with a family of inclusion maps $\{ \iota_i\colon \mathbf{A}_i
  \to \mathbf{A} \}_{i \in I}$. If for any BA $\mathbf{B}$ with a family of
  homomorphisms $\{ f_i\colon \mathbf{A} \to \mathbf{B} \}_{i \in I}$ there
  exists a unique common extension of $\{ f_i\colon \mathbf{A} \to \mathbf{B}
  \}_{i \in I}$ ($f\colon \mathbf{A} \to \mathbf{B}$ in the diagram),
  \[
    \begin{tikzcd}
      \mathbf{A}_i \arrow{r}{\iota_i} \arrow{rd}[swap]{f_i} & \mathbf{A} \arrow[d,dashed,"f"] \\
      & \mathbf{B}
    \end{tikzcd}
  \]
  then $\mathbf{A}$ is the \emph{internal sum}\footnote{It is also known as the
    \emph{free product} and as the coproduct in the category of BAs.} of $\{
  \mathbf{A}_i \}_{i \in I}$. We will denote it as $\bigoplus_{i \in I}
  \mathbf{A}_i$.
\end{definition}
